Manuscript

### 2019-01-07 manuscript.Rmd

At an $\alpha =  0.05$, no DGLs were identified in the CCLE screen when using mutation status as a correlate (n = 7), but CTRP and GDSC identified six and five, respectively, in skin cancer, lung cancer, and cancer. These significant associations did not hold after Bonferroni correction in CTRP ($n = 48$, $\alpha_{adjusted} = 0.001$) or GDSC ($n = 39$, $\alpha_{adjusted} = 0.001$).

>>>>

At an $\alpha =  0.05$, no DGLs were identified in the CCLE screen when using mutation status as a correlate (*n = 7*), but CTRP and GDSC identified *six* and *five*, respectively, in skin cancer, lung cancer, and cancer. These significant associations did not hold after Bonferroni correction in CTRP ($n = 48$, $\alpha_{adjusted} = 0.001$) or GDSC ($n = 39$, $\alpha_{adjusted} = 0.001$).
